---
title: "Untitled"
author: "Paul Oldham"
date: "01/04/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains the scripts for importing data from Spark into R. Later chunks show the workings for obtaining additional information from MAG on the Spark cluster from the Lens data using paperids. Specifically, the code to obtain the affiliation data from MAG.

## Kenya import papers

```{r}
library(tidyverse)
library(sparklyr)
# establish a spark connection

sc <- spark_connect(master = "local")

spark_read_parquet(sc, "kenya_papers", "kenya_papers_spark_tbl")

kenya_papers_tbl <- tbl(sc, "kenya_papers")

kenya_papers_tbl %>% count() # 62,095

kenya_papers <- collect(kenya_papers_tbl)
```


edit the names from the joins

```{r}
names(kenya_papers)
```

```{r}
kenya_papers <- kenya_papers %>% rename(rankno = `rankno.x`, organisation_citation = `citationcount.x`, paper_citation = `citationcount.y`) %>% select(-`rankno.y`, -`createddate.x`, -`createddate.y`)

write_csv(kenya_papers, "kenya_papers.csv")
```

```{r}
spark_read_parquet(sc, "kenya_fos", "kenya_fosid_spark_tbl")

kenya_fos_tbl <- tbl(sc, "kenya_fos")

kenya_fos_tbl %>% count() # 255497

kenya_fos <- collect(kenya_fos_tbl)
```

# Join to FOS table here

a) import the fos table and copy to spark
b) make the join on fieldofstudy id

```{r}
# note that this overwrites the original table
kenya_fos <- inner_join(kenya_fos, fos, by = "fieldofstudyid")

write_csv(kenya_fos, "kenya_fos.csv")
```


### Read in Authors

This table refers to authors associated with a Kenya affiliation (source table is affiliation with GRID) and filtered to Kenya. 

```{r}
spark_read_parquet(sc, "kenya_papers_authors", "kenya_papers_authors_spark_tbl")

kenya_authors_tbl <- tbl(sc, "kenya_papers_authors")

kenya_authors_tbl %>% count() # 62095

kenya_authors <- collect(kenya_authors_tbl)
```

## Lenslit data

The lens provides the Microsoft Academic Graph paperid but does not provide the 

- author affiliation 
- author names (except as a concatenated list)
- it does provide the field of study

So, we want to access the author affiliation information in particular

```{r}
# imported paperid as character when should be numeric

kenlenslit_paperid <- tbl(sc, "kenya_lenslit_paperid") %>% 
  mutate(paperid = as.numeric(paperid))

kenya_lenslit_affiliation_papers <- inner_join(kenlenslit_paperid, affiliation_papers, by = "paperid")

spark_write_table(kenya_lenslit_affiliation_papers, "kenya_lenslit_affiliation_papers_tbl")

affiliations_grid <- tbl(sc, "affiliations_grid_spark_tbl")

kenya_lenslit_affiliations_grid_papers <- inner_join(kenya_lenslit_affiliation_papers, affiliations_grid, by = "affiliationid")

spark_write_table(kenya_lenslit_affiliations_grid_papers, "kenya_lenslit_affiliations_grid_papers_tbl")

authors <- tbl(sc, "authors_spark_tbl")

kenya_lenslit_authors <- inner_join(kenya_lenslit_affiliation_papers, authors, by = "authorid")

spark_write_table(kenya_lenslit_authors, "kenya_lenslit_authors_tbl")
```

### Read in extra lens data

The lens paper ids were read into the MAG Spark cluster to retrieve the affiliation data and author tables.

Note that the input of paperids and the output are not the same and this requires investigation and clean up. 

```{r}
spark_read_parquet(sc, "kenya_lenslit_affiliation_papers", "kenya_lens/kenya_lenslit_affiliation_papers_tbl")

kenlenslit_affiliation_papers <- tbl(sc, "kenya_lenslit_affiliation_papers") %>% collect()

write_csv(kenlenslit_affiliation_papers, "kenya_lens/kenlens_affiliation_papers.csv") 
```

```{r}
spark_read_parquet(sc, "kenya_lenslit_affiliations_grid_papers", "kenya_lens/kenya_lenslit_affiliations_grid_papers_tbl")

kenlenslit_affiliation_grid <- tbl(sc, "kenya_lenslit_affiliations_grid_papers") %>% collect()

write_csv(kenlenslit_affiliation_grid, "kenya_lens/kenlens_affiliations_grid.csv") 
```

```{r}
spark_read_parquet(sc, "kenya_lenslit_authors", "kenya_lens/kenya_lenslit_authors_tbl")

kenlenslit_authors <- tbl(sc, "kenya_lenslit_authors") %>% collect()

write_csv(kenlenslit_authors, "kenya_lens/kenlens_authors.csv")
```